\section{Robot Operation System 2 (ROS2)}

Starting this project we had a wish from our customer to use ROS2 for our middleware. In earlier iterations of Local Hawk, they have used ROS1 as their middleware, and now that ROS2 have a larger community and support they are now interested in implementing ROS2 for upcoming projects. 

We have not looked into any other middleware other than ros, due to the fact that ros is the most used and standard robotic middleware. \cite{ros2standard}

\subsection{ROS2 vs ROS1}
In the course of our research, we have conducted extensive testing on ROS2, while our understanding of ROS1 is primarily derived from literature references. Our findings, combined with the referenced material, lead us to conclude that ROS2 exhibits several superiorities over ROS1.

ROS1's primary limitation is its lack of real-time communication capability, something that ROS2 supports. \cite{ros2real}

Unlike ROS1, which requires a centralized system (ROS Master) for operation, ROS2 nodes can function independently on different machines. Furthermore, ROS2 introduces essential security features, such as authorization, absent in ROS1. It's also important to note that ROS2 is compatible with more recent Python versions (3.5 and above), while ROS1 primarily targets the older Python 2. \cite{ros2perform}

The potential applications of ROS2 are diverse, including autonomous vehicles, industrial automation, and robotics research. The real-time communication capability of ROS2 makes it particularly suitable for autonomous vehicles. Its seamless integration with cloud resources is beneficial for industrial automation, while its advanced security features are advantageous for robotics research involving sensitive data.



\section{}