Our bachelor's project aimed to provide readers with valuable insights into edge image processing for lightweight unmanned aerial vehicles (UAVs). Through our research and experimentation, we successfully achieved object detection capabilities tailored specifically for such UAVs. We utilized four different hardware and software configurations to accomplish this task.

By benchmarking our four configurations, we assessed their respective detection accuracy and frame-per-second (FPS) performance on a single object. This allowed us to comprehensively evaluate the suitability and effectiveness of each configuration for lightweight UAVs in terms of precision and real-time processing capabilities.

Our findings not only contribute to the field of edge image processing but also hold practical significance for the Local Hawk Project and its endeavors. The results highlight the importance of selecting appropriate hardware and software configurations to achieve optimal object detection performance within the constraints of lightweight UAVs.

Furthermore, this project serves as a foundation for future research and development in the area of edge image processing for lightweight UAVs. The insights gained from our study can guide further improvements in detection accuracy and FPS, leading to enhanced capabilities for lightweight UAVs in various domains, including surveillance, monitoring, and search-and-rescue operations.

Overall, our project successfully addresses the goal of providing the reader with knowledge on edge image processing for lightweight UAVs. Through our experimentation and evaluation, we have demonstrated the feasibility and efficacy of object detection using different configurations, thereby contributing to the advancement of lightweight UAV technologies and applications.